---
title: "Simplex and Augmented Lattice Designs"
---

Other Design Types that you should be aware of include the Simplex Lattice designs, illustrated below:

```{r, linear}
#| echo: false
#| warning: false
#| message: false
#| fig-out: 30%
#| fig-asp: 0.618
library(mixexp2)

des1 <- mixexp::SLD(3, 1)
plot1 <- mixexp::DesignPoints(des1)
```



```{r, quadratic}
#| echo: false
#| warning: false
#| message: false
#| fig-out: 30%
#| fig-asp: 0.618
des2 <- mixexp::SLD(3, 2)
plot2 <- mixexp::DesignPoints(des2)
```

```{r, cubic}
#| echo: false
#| warning: false
#| message: false
#| fig-out: 30%
#| fig-asp: 0.618
des3 <- mixexp2::SLDnew(3, 3, center=F)
plot3 <- mixexp::DesignPoints(des3)
```


```{r, all}
#| echo: false
#| warning: false
#| message: false
#| label: fig-mpg
#| fig-show: hold
#| fig-cap: "Different Mixture Designs"
#| fig-subcap:
#|   - "Degree 1"
#|   - "Degree 2"
#|   - "Degree 3"
#| layout-ncol: 3
#| fig-out: 30%
#| fig-asp: 0.618 
plot1
plot2
plot3

```


The number and position of points determines the order of the regression equation. The linear model only allow terms in the main components to be evaluated:

$$\hat{y}=\beta_1x_1+\beta_2x_2+\beta_3x_3$$

(notice that there is no mean term $\beta_0$ in the regression equation)

The quadratic model includes the two-way interactions:

$$\hat{y}=\beta_1x_1+\beta_2x_2+\beta_3x_3+\beta_{12}x_1x_2+\beta_{13}x_1x_3+\beta_{23}x_2x_3$$

The cubic, and special cubics, include three-way interactions. The 'special cubic' omits some of the possible interactions.


### Augmented Lattice

The lattices can be augmented with interior points. A Degree 2 Simplex Lattice augmented with interior points, including a center point:

```{r}
#| echo: false
#| warning: false
#| message: false
library(mixexp2)
des <- mixexp2::SLDnew(3, 2, center=T, axial=T)
mixexp::DesignPoints(des)
```


This model allows the interior of the triangle to be explored properly.
